DIAGNOSTIC SUPPORT OF SKIN LESION CLASSIFICATION USING CNN AND SOFT ATTENTION

### 2022-06-24 MDPI/Sensor Paper/template.tex
Update MDPI

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}
% Reference 1
\bibitem[Author1(year)]{ref-journal}
Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
\bibitem[Author2(year)]{ref-book1}
Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
% Reference 3
\bibitem[Author3(year)]{ref-book2}
Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
% Reference 4
\bibitem[Author4(year)]{ref-unpublish}
Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
% Reference 5
\bibitem[Author5(year)]{ref-communication}
Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
% Reference 6
\bibitem[Author6(year)]{ref-proceeding}
Author 1, A.B.; Author 2, C.D.; Author 3, E.F. Title of presentation. In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
% Reference 7
\bibitem[Author7(year)]{ref-thesis}
Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
% Reference 8
\bibitem[Author8(year)]{ref-url}
Title of Site. Available online: URL (accessed on Day Month Year).
\end{thebibliography}

>>>>

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}

\bibitem[Author1(year)]{08332}
Katherine M. Li and Evelyn C. Li. Skin Lesion Analysis Towards Melanoma Detection via End-to-end Deep Learning of Convolutional Neural Networks. {\em Journal Abbreviation} {\bf 2018}.

\bibitem[Author2(year)]{03225}
Xiaohan Xing and Yuenan Hou and  Hang Li and Yixuan Yuan and Hongsheng Li and Max Q.-H. Meng Categorical Relation-Preserving Contrastive Knowledge Distillation for Medical Image Classification. {\em Journal Abbreviation} {\bf 2021}.

\bibitem[Author2(year)]{03798}
Rishu Garg and Saumil Maheshwari and Anupam Shukla Decision Support System for Detection and Classification of Skin Cancer using CNN. {\em Journal Abbreviation} {\bf 2019}.

\bibitem[Author2(year)]{09365}
Amirreza Rezvantalab and Habib Safigholi and Somayeh Karimijeshni Dermatologist Level Dermoscopy Skin Cancer Classification Using Different Deep Learning Convolutional Neural Networks Algorithms. {\em Journal Abbreviation} {\bf 2020}.

\bibitem[Author2(year)]{10348}
Amirreza Rezvantalab and Habib Safigholi and Somayeh Karimijeshni Dermatologist Level Dermoscopy Skin Cancer Classification Using Different Deep Learning Convolutional Neural Networks Algorithms. {\em Journal Abbreviation} {\bf 2021}.

\bibitem[Author2(year)]{06612}
Kyle Young and Gareth Booth and Becks Simpson and Reuben Dutton and Sally Shrapnel Dermatologist Level Dermoscopy Deep neural network or dermatologist?. {\em Journal Abbreviation} {\bf 2021}.

\end{thebibliography}
